\textls[-0]{\thetitle}

### 2023-03-14 canonicitymodel.tex
Fixing syn translation
Shift back to original version of the canonicity model.

\newcommand{\Set}[1]{\ensuremath{\texttt{Set}_{#1}}}

{\textbf{Set-theoretic Universe Assumption.}} As a simplifying move, we assume an infinite hierarchy of Grothendieck universes $\Set{i}$ for $i \in \mathbb{N}$ in our meta-logic.

For people familiar with Agda, we can roughly consider Grothendieck Universe $\Set{i}$ as the $\Set{i}$ in Agda. In other words, each $\Set{i}$ is 
\begin{itemize}
  \item Closed under dependent function type and dependent tuple type. For example, when we have $\denotesC{A}, \denotes{B} \in \Set{i}$, we will have $\denotes{\TyPi{A}{B}} \in \Set{i}$
  \item the hierarchy is cumulative as $\Set{i} \in \Set{i+1}$ and $\Set{i} \subseteq \Set{i+1}$
\end{itemize}

@@

\begin{align*}
  \denotesC{\goodCtx{\Gm}{i}} & \text{ is a Set of closed substitution} \goodSub{\cdot}{\_}{\Gm} \\
  % &\text{and we define } \goodCtxS{\Gm}{i} :\iff \denotesC{\goodCtx{\Gm}{i}} \text{ is defined} \\
  \denotesC{\goodType{\Gm}{T}{}} & \text{ is a function maps to Set s.t.} \\
  & \text{for arbitrary } \gm \in \denotesC{\goodCtx{\Gm}{}}, \denotesC{\goodType{\Gm}{T}{}}(\gm) \text{ is a Set of closed terms } \goodTerm{\cdot}{\_}{\sub{T}{\gm}} \\ 
  % &\text{and we define } \goodTypeS{\Gm}{T}{i} : \iff \denotesC{\goodType{\Gm}{T}{i}} \text{ is defined } \\ 
  \denotesC{\goodSub{\Gm}{\gm}{\Delta}} & \text{ is a function}: \denotesC{\goodCtx{\Gm}{i}} \to \denotesC{\goodCtx{\Delta}{i}} \text{ s.t. } \denotesC{\goodSub{\Gm}{\gm}{\Delta}}(\sigma) \coloneqq \SubstComp{\sigma}{\gm} \\
  % &\text{and we define } \goodSubC{\Gm}{\gm}{\Delta} :\iff \denotesC{\goodSub{\Gm}{\gm}{\Delta}} \text{ is defined} \\
  \denotesC{\goodTerm{\Gm}{t}{T}} & \text{ is a dependent function}: \prod_{\gm \in \denotesC{\goodCtx{\Gm}{i}}}\denotesC{\goodType{\Gm}{T}{}}(\gm)  \text{ s.t. } \denotesC{\goodTerm{\Gm}{t}{T}}(\gm) \coloneqq \sub{t}{\gm} \\
  \denotesC{\goodType{\Gm}{\top}{}}(\gm) &= \{t : t \equiv \unit \} \\
  \denotesC{\goodType{\Gm}{\bot}{}}(\gm) &= \emptyset \\
  \denotesC{\goodType{\Gm}{\cB}{}}(\gm) &= \{t : t \equiv \true \text{ or } t \equiv\false \} \\
  \denotesC{\goodType{\Gm}{\TyId{a}{b}}{}}(\gm) &= \{t : t \equiv \eqrefl{\sub{a}{\gm}} \} \text{ when } \sub{a}{\gm} \equiv \sub{b}{\gm} \\ 
  &= \emptyset \text{ otherwise } \\ 
  \denotesC{\goodType{\Gm}{\TyPi{A}{B}}{}} &= \\
  \denotesC{\goodType{\Gm}{\TySigma{A}{B}}{}} &= \\
  \denotesC{\goodCtx{\cdot}{}} &= \{\SubstEmp\} \text{  the singleton set with identity substitution} \\ 
  \denotesC{\goodCtx{\Gm, T}{}} &= \{ (\gamma , t) : \gamma \in \denotesC{\goodCtx{\Gm}{}}, t \in \denotesC{\goodType{\cdot}{\sub{T}{\gm}}{}}  \} \\
  \denotesC{\goodTerm{\Gm}{\unit}{\top}}(\gm) &= \unit\\
  \denotesC{\goodTerm{\Gm}{\true}{\cB}}(\gm) &= \true \\
  \denotesC{\goodTerm{\Gm}{\false}{\cB}}(\gm) &= \false \\
  \denotesC{\goodTerm{\Gm}{\ifb{c}{a}{b}}{T}}(\gm) &= \denotesC{a}(\gm) \text{ if } \denotes{c}(\gm) \equiv \true \\
  \denotesC{\goodTerm{\Gm}{\ifb{c}{a}{b}}{T}}(\gm) &= \denotesC{b}(\gm) \text{ if } \denotes{c}(\gm) \equiv \false \\
  \denotesC{\goodTerm{\Gm}{\eqrefl{t}}{\TyId{t}{t}}}(\gm) &= \eqrefl{\sub{t}{\gm}}\\
  \denotesC{\goodTerm{\Gm}{\lam{t}}{\TyPi{A}{B}}} &= \\
  \denotesC{\goodTerm{\Gm}{\app{t}}{B}} &= \\
  \denotesC{\goodTerm{\Gm}{\pair{a}{b}}{\TySigma{A}{B}}} &= \\
  \denotesC{\goodTerm{\Gm}{\fst{t}}{T}} &= \\
  \denotesC{\goodTerm{\Gm}{\snd{t}}{T}} &= \\
\end{align*}

>>>>

\newcommand{\Set}[1]{\ensuremath{\texttt{Set}_{#1}}}
\newtheorem{assumption}{Assumption}[section]

\begin{assumption}[Set-theoretic Universe Assumption] As a simplifying move, we assume an infinite hierarchy of Grothendieck universes $\Set{i}$ for $i \in \mathbb{N}$ in our ambient meta-logic.
\end{assumption}

We can roughly consider each Grothendieck Universe $\Set{i}$ as a $\Set{i}$ in Agda. In other words, each $\Set{i}$ is 
\begin{itemize}
  \item Closed under dependent function type and dependent tuple type. For example, later, for our interpretation of dependent function type, when we have $\denotesC{A}, \denotesC{B} \in \Set{i}$, we will have $\denotesC{\TyPi{A}{B}} \in \Set{i}$
  \item the hierarchy is cumulative as $\Set{i} \in \Set{i+1}$ and $\Set{i} \subseteq \Set{i+1}$
\end{itemize}

@@

\begin{align*}
  \denotesC{\goodCtx{\Gm}{k}} & \text{ is a Set of closed substitution} \goodSub{\cdot}{\_}{\Gm} \\
  % &\text{and we define } \goodCtxS{\Gm}{i} :\iff \denotesC{\goodCtx{\Gm}{i}} \text{ is defined} \\
  \denotesC{\goodType{\Gm}{T}{j}} & \text{ is a function maps to $\Set{j}$ s.t.} \\
  & \text{for arbitrary } \gm \in \denotesC{\goodCtx{\Gm}{}}, \denotesC{\goodType{\Gm}{T}{}}(\gm) \text{ is a an element of } \Set{j}  \\ 
  % &\text{and we define } \goodTypeS{\Gm}{T}{i} : \iff \denotesC{\goodType{\Gm}{T}{i}} \text{ is defined } \\ 
  \denotesC{\goodSub{\Gm}{\gm}{\Delta}} & \text{ is a function}: \denotesC{\goodCtx{\Gm}{i}} \to \denotesC{\goodCtx{\Delta}{i}} \text{ s.t. } \denotesC{\goodSub{\Gm}{\gm}{\Delta}}(\sigma) \coloneqq \SubstComp{\sigma}{\gm} \\
  % &\text{and we define } \goodSubC{\Gm}{\gm}{\Delta} :\iff \denotesC{\goodSub{\Gm}{\gm}{\Delta}} \text{ is defined} \\
  \denotesC{\goodTerm{\Gm}{t}{T}} & \text{ is a dependent function}: \prod_{\gm \in \denotesC{\goodCtx{\Gm}{i}}}\denotesC{\goodType{\Gm}{T}{}}(\gm)  \text{ s.t. } \denotesC{\goodTerm{\Gm}{t}{T}}(\gm) \coloneqq \sub{t}{\gm} \\
  \denotesC{\goodType{\Gm}{\top}{}}(\gm) &= \{t : t \equiv \unit \} \\
  \denotesC{\goodType{\Gm}{\bot}{}}(\gm) &= \emptyset \\
  \denotesC{\goodType{\Gm}{\cB}{}}(\gm) &= \{t : t \equiv \true \text{ or } t \equiv\false \} \\
  \denotesC{\goodType{\Gm}{\TyId{a}{b}}{}}(\gm) &= \{t : t \equiv \eqrefl{\sub{a}{\gm}} \} \text{ when } \sub{a}{\gm} \equiv \sub{b}{\gm} \\ 
  &= \emptyset \text{ otherwise } \\ 
  \denotesC{\goodType{\Gm}{\TyPi{A}{B}}{}} &= \\
  \denotesC{\goodType{\Gm}{\TySigma{A}{B}}{}} &= \\
  \denotesC{\goodCtx{\cdot}{}} &= \{\SubstEmp\} \text{  the singleton set with identity substitution} \\ 
  \denotesC{\goodCtx{\Gm, T}{}} &= \{ (\gamma , t) : \gamma \in \denotesC{\goodCtx{\Gm}{}}, t \in \denotesC{\goodType{\cdot}{\sub{T}{\gm}}{}}  \} \\
  \denotesC{\goodTerm{\Gm}{\unit}{\top}}(\gm) &= \unit\\
  \denotesC{\goodTerm{\Gm}{\true}{\cB}}(\gm) &= \true \\
  \denotesC{\goodTerm{\Gm}{\false}{\cB}}(\gm) &= \false \\
  \denotesC{\goodTerm{\Gm}{\ifb{c}{a}{b}}{T}}(\gm) &= \denotesC{a}(\gm) \text{ if } \denotes{c}(\gm) \equiv \true \\
  \denotesC{\goodTerm{\Gm}{\ifb{c}{a}{b}}{T}}(\gm) &= \denotesC{b}(\gm) \text{ if } \denotes{c}(\gm) \equiv \false \\
  \denotesC{\goodTerm{\Gm}{\eqrefl{t}}{\TyId{t}{t}}}(\gm) &= \eqrefl{\sub{t}{\gm}}\\
  \denotesC{\goodTerm{\Gm}{\lam{t}}{\TyPi{A}{B}}} &= \\
  \denotesC{\goodTerm{\Gm}{\app{t}}{B}} &= \\
  \denotesC{\goodTerm{\Gm}{\pair{a}{b}}{\TySigma{A}{B}}} &= \\
  \denotesC{\goodTerm{\Gm}{\fst{t}}{T}} &= \\
  \denotesC{\goodTerm{\Gm}{\snd{t}}{T}} &= \\
  \denotesC{\goodType{\Gm}{\cU_j}{j}}(\gm) &= \{t : \goodTerm{\cdot}{t}{\El{T}}\} \quad \text{     for some } \goodTerm{\cdot}{T}{\cU_j}  \\
  \denotesC{\goodTerm{\Gm}{\codety{T}}{\cU_j}}(\gm) &= \denotesC{T}(\gm) \\ 
  \denotesC{\goodType{\Gm}{\El{T}}{j}}(\gm) &= \denotesC{T}(\gm) \\
\end{align*}
